---
title: "Lab06 - multiple comparisons"
output: pdf_document
---

## Goals

The goal in this lab is to practice finding familywise conidence intervals for multiple comparisons.

## Loading packages

Here are some packages with functionality you may need for this lab.  Run this code chunk now.

```{r}
library(readr)
library(ggplot2)
library(gridExtra)
library(mosaic)
library(dplyr)
library(gmodels)

options("pillar.sigfig" = 10) # print 10 significant digits in summarize output

longevity <- read_csv("http://www.evanlray.com/data/sleuth3/ex0501_longevity.csv") %>%
  mutate(
    Diet = factor(Diet, levels = c("NP", "N/N85", "N/R50", "R/R50", "lopro", "N/R40"))
  )

nrow(longevity)
```

#### Find the multiplier that would be used for Bonferroni 95% familywise intervals for 5 comparisons based on this data set.

```{r}

```

#### Find the multiplier that would be used for Scheffe 95% familywise intervals for 5 comparisons based on this data set.

```{r}

```


#### Find familywise 95% Confidence Intervals

The code below finds individual 95% confidence intervals for the 5 differences in group means the researchers planned for this study.  For each, add calculations of appropriately adjusted Bonferroni and Scheffe familywise intervals.

```{r}
anova_fit <- lm(Lifetime ~ Diet, data = longevity)
```

#### (a) $H_0: \mu_2 = \mu_3$ vs $H_A: \mu_2 \neq \mu_3$.  Are the population mean lifetimes the same for the \textbf{N/N85} and \textbf{N/R50} groups?

```{r}
fit.contrast(anova_fit, "Diet", c(0, 1, -1, 0, 0, 0), conf.int = 0.95)
```

#### (b) $H_0: \mu_3 = \mu_4$ vs $H_A: \mu_3 \neq \mu_4$.  Are the population mean lifetimes the same for the \textbf{N/R50} and \textbf{R/R50} groups?

```{r}
fit.contrast(anova_fit, "Diet", c(0, 0, 1, -1, 0, 0), conf.int = 0.95)
```

#### (c) $H_0: \mu_3 = \mu_6$ vs $H_A: \mu_3 \neq \mu_6$.  Are the population mean lifetimes the same for the \textbf{N/R50} and \textbf{N/R40} groups?

```{r}
fit.contrast(anova_fit, "Diet", c(0, 0, 1, 0, 0, -1), conf.int = 0.95)
```

#### (d) $H_0: \mu_3 = \mu_5$ vs $H_A: \mu_3 \neq \mu_5$.  Are the population mean lifetimes the same for the \textbf{N/R50} and \textbf{N/R50} lopro groups?

```{r}
fit.contrast(anova_fit, "Diet", c(0, 0, 1, 0, -1, 0), conf.int = 0.95)
```

#### (e) $H_0: \mu_2 = \mu_1$ vs $H_A: \mu_2 \neq \mu_1$.  Are the population mean lifetimes the same for the \textbf{N/N85} and \textbf{NP} groups?

```{r}
fit.contrast(anova_fit, "Diet", c(-1, 1, 0, 0, 0, 0), conf.int = 0.95)
```

#### What is the interpretation of the individual 95% confidence interval obtained in part (a) from the fit.contrast function?



#### What is the interpretation of the Bonferroni intervals?  


